\documentclass[a5paper,10pt]{article}
\usepackage[english]{babel}

% maths packages
\usepackage{mathtools,commath,amsthm,amssymb,thmtools}

% code
\usepackage{minted}

% Document-wide formatting
\usepackage{geometry}
\usepackage{enumitem}
\linespread{1.05}
\setlist{noitemsep}

% links
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
  colorlinks,
  linkcolor={red!50!black},
  citecolor={blue!50!black},
  urlcolor={blue!80!black}
}

% Fonts
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}  % better spacing
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

\title{Diary}
\author{Conor Reynolds}
\date{}

\begin{document}
    \maketitle

    \section*{2017-09-21}

    Pretty much decided to use the `pipes' library for data streaming. As for graphics packages, so far we have:

    % add links to these
    \begin{itemize}
        \item gloss
        \item dynamic-plot
        \item dynamic-graph
        \item Chart
        \item diagrams
        \item typed-spreadsheet
        \item plain OpenGL bindings
    \end{itemize}

    Going ahead with using gloss, mainly for ease of use (esp. since I have no prior background in any kind of graphics programming).

    \section*{2017-09-22}

    Decided to use Haskell's STM library to handle shared mutable state between gloss and the rest of the program. A gloss process is kicked-off with access to a TVar, which is modified by a pipe that continuously reads data from stdin (one line at a time). All it does, currently, is plot a stream of $ x,y $-coordinates onto a blank, white canvas.

    \section*{2017-09-24 --- 2017-09-25}

    On a new branch, \verb|anim->play| (which was, in hindsight, not a very good name for a branch), began the migration from the animateIO function to the playIO function to allow for custom event handling, which is no doubt needed. This lead to creating a barebones MVC-style backend, which should allow for much more complex features to be added in the future.

    \section*{2017-09-26}

    Merged \verb|anim->play| with \verb|master|. Work has begun on a new branch, \verb|axes|. This will deal primarily with drawing the axes, although it may end up involving writing a more robust view framework. Inside the viewport, you can have any number of `frames', which are distinct viewing areas, each having their own dataset, zoom level, styles, etc.

    \section*{2017-10-21}

    After lots of quiet experimentation, cplot now uses
    \begin{itemize}
        \item gtk3 and frpnow as GUI backend
        \item Chart library for defining charts
        \item Cairo for rendering charts to gtk3 widgets
    \end{itemize}
    Multiple other options were explored:
    \begin{itemize}
        \item External JS libs for charting (chart, plotly, epoch), communicating with a Haskell process via websockets
        \item HaskellR
        \item Some other arbitrary external process communicating via zeromq / nanomsg or some other messaging protocol
    \end{itemize}
    All had multiple problems that were more or less irreconcilable given the aim of this project, but importantly they were all a bit too slow for fast real-time data visualisation. The current approach (modulo a better system for managing large amounts of data) is vastly more efficient than any other approach attempted so far.
    
    \section*{2017-10-25}
    
    In the interest of code maintainability, cplot now uses what has been referred to by Michael Xavier in his \href{https://michaelxavier.net/posts/2016-04-03-Enterprise-Haskell-Pattern-Lensed-Reader.html}{blog post} as the `lensed reader' pattern (Michael Snoyman also \href{https://www.fpcomplete.com/blog/2017/06/readert-design-pattern}{discusses} what is effectively the same idea). As of this writing, the code base is quite hacky and hardcoded to see whether it would work. It does, thankfully.
    
    \section*{2017-10-31}
    
    Most of the codebase is finally at a stage where I'm not deeply embarrassed for it being publicly viewable.
    
    Eventually got around to abstracting the chart API into its own module, so work on new features can begin very soon (see commit 8b72826 on master for details). Lens based functionality has also been improved (all instances of \verb|makeFields| have been changed to \verb|makeClassy|, seems to compose a lot better), and simple exception handling was added, so you don't have to mash Ctrl-C every time something goes wrong.
    
    \section*{2017-11-01}
    
    Fixed an issue with the behaviour of the stdin pipe from pipes-bytestring. It doesn't automatically chunk by by lines. Combined with the fact that we were throwing away parse errors, this caused a lot of strange behaviour:
    \begin{itemize}
        \item If the consumer blocked the producer, the producer would build a large multi-line buffer, which it would then send all at once through the pipeline: the parser would then parse the first line it saw, ignore the rest, and pipe it through to the consumer (this is why you would occasionally see what initially appeared to be a graphical glitch where certain data points were ignored and the inbetween was just connected with a straight line).
        \item If the consumer happened to ask for data `too early,' it appeared the producer was perfectly happy to supply that data, meaning the program would occasionally have to parse garbled half-lines, which (as of the last patch) caused the program to crash.
    \end{itemize}
    For a hilarious demonstration of both issues, try the Python examples with no time delay on some commit before the pipes-bug merge with master.
    
    It seems pipes-text has the required capability to split a stream by lines (in fact it's probably a better idea, at least semantically, to use text over bytestring here), but currently the fix uses conduit and bytestrings. I'll be experimenting with different solutions before merging anything with master.
\end{document}
